FAIR Theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2024-12-06 manuscript.Rmd
update 2024-12-06 13:12:45.606398

## FAIR Theory and Recognition & Rewards

FAIR theory provides a clear deliverable, and a clear goal, for scholars and institutions seeking to promote contributions to theory.
In the spirit of DORA, this helps researchers obtain credit for their theoretical contributions - obviating the necessity of publishing a purely theoretical paper, which can be challenging.

>>>>

<!-- ## FAIR Theory and Recognition & Rewards -->

<!-- FAIR theory provides a clear deliverable, and a clear goal, for scholars and institutions seeking to promote contributions to theory. -->
<!-- In the spirit of DORA, this helps researchers obtain credit for their theoretical contributions - obviating the necessity of publishing a purely theoretical paper, which can be challenging. -->
